\large{\bf Looking forwards and backwards through locally regulated populations }

### 2023-01-13 forwards-and-backwards.tex
.

    To get around this,
    first note that both $b$ and $c$ are uniformly bounded above since $\gamma$, $r$ and $F$ are.
    Also note that by \plr{TODO},
    for any $\delta > 0$ we can find a $K$ such that
    $$
    \IP\left\{
        \sup_{0 \le t \le T} \sup_x \smooth{F} \eta_t(x) < K
        \right\} < \delta,
    $$
    uniformly in $N$ and over a compact set of initial conditions.
    Since $F$ is uniformly continuous, this implies that $\sup_{0 \le t \le T} \sup_x F(x, \eta_t)$
    is similarly tight,
    as well as the rate of downward drift of the level of a line of descent,
    i.e., there is a $\bar b$ such that $b(x, \eta_t) \le \bar b$
    on a set of probability at least $1-\delta$ as well.
    Therefore, if $u_1 \ge u_0 + \bar b T$, then
    $$
    \IP\left\{
        \inf_{0 \le t \le T} U_a(t) \le u_0
        \;\big|\;
        U_a(0) > u_1
    \right\}
    \le \delta ,
    $$
    and so with high probability any lines of descent that had level below $u_0$
    at some point $0 \le t \le T$
    are descended from lines of descent with initial level below $u_1$.
    Since the number of lines of descent with level below $u_1$
    converges to a Poisson with finite mean,
    we need only show that the number of offpring lines of descent
    produced by this initially finite number is also tight.
    However, this follows immediately
    since the rate of production of new lines of descent with level below $u_1$
    of a line of descent at location $x$ and level $u$ is
    $2 (u_1 - u) N^{-1} \theta \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy)$
    and therefore uniformly bounded (because we may take $u_1 \le N$).

@@

We now introduce two important theorems on compactness and convergence in the vague topology.
\begin{theorem}[Theorem A.23 in \cite{kallenberg1997foundations}]
For any locally compact, second-countable Hausdorff Space $S$, 
we have
\begin{itemize}
\item $\mathcal{S}$ is Polish in the vague topology,
\item a set $A\subset \mathcal{S}$ is vaguely relatively compact iff $\sup_{\mu\in A} \mu f < \infty$ for all $f \in C^{+}_{c}$
\item if $\mu_n \to \mu$ in the vague topology and $B \in \hat{S}$ with $\mu \partial B = 0$, then $\mu_n B \to \mu B$
\end{itemize}
\end{theorem}

>>>>

    To get around this,
    first note that both $b$ and $c$ are uniformly bounded above 
    by Lemma~\ref{lem:gamma_bound} and since $\gamma$, $r$, $F$ \comment{(???)}, and $\theta/N$ are.
    Also note that for any $\delta > 0$ we can find a $K$ such that
    $$
    \IP\left\{
        \sup_{0 \le t \le T} \sup_x \smooth{F} \eta_t(x) < K
        \right\} < \delta,
    $$
    uniformly in $N$ and over a compact set of initial conditions.
    Since $F$ is uniformly continuous, this implies that $\sup_{0 \le t \le T} \sup_x F(x, \eta_t)$
    is similarly tight,
    as well as the rate of downward drift of the level of a line of descent,
    i.e., there is a $\bar b$ such that $b(x, \eta_t) \le \bar b$
    on a set of probability at least $1-\delta$ as well.
    Therefore, if $u_1 \ge u_0 + \bar b T$, then
    $$
    \IP\left\{
        \inf_{0 \le t \le T} U_a(t) \le u_0
        \;\big|\;
        U_a(0) > u_1
    \right\}
    \le \delta ,
    $$
    and so with high probability any lines of descent that had level below $u_0$
    at some point $0 \le t \le T$
    are descended from lines of descent with initial level below $u_1$.
    Since the number of lines of descent with level below $u_1$
    converges to a Poisson with finite mean,
    we need only show that the number of offpring lines of descent
    produced by this initially finite number is also tight.
    However, this follows immediately
    since the rate of production of new lines of descent with level below $u_1$
    of a line of descent at location $x$ and level $u$ is
    $2 (u_1 - u) N^{-1} \theta \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy)$
    and therefore uniformly bounded (because we may take $u_1 \le N$).

@@

We now introduce two important theorems on compactness and convergence in the vague topology.
\begin{theorem}[Theorem A.23 in \cite{kallenberg1997foundations}]
For any locally compact, second-countable Hausdorff Space $S$, 
we have
\begin{itemize}
\item $\mathcal{M}(S)$ is Polish in the vague topology,
\item a set $A\subset \mathcal{M}(S)$ is vaguely relatively compact iff $\sup_{\mu\in A} \mu f < \infty$ for all $f \in C^{+}_{c}$
\item if $\mu_n \to \mu$ in the vague topology and $B \in \hat{S}$ with $\mu \partial B = 0$, then $\mu_n B \to \mu B$
\end{itemize}
\end{theorem}
